Exploratory Data Analysis

### 2019-09-11 hw1/results/Exploratory Data Analysis.Rmd
More work on EDA

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

@@

```{r}
plot_me <- function(d, title, xlab, ylab){
  nas <- d %>% filter(is.na(x)) %>% nrow()
  density <- d %>%
    filter(!is.na(x)) %>%
    ggplot(., aes(x, stat(count))) +
    geom_density() +
    labs(title = title, 
       x = xlab,
       y = ylab) +
    theme(panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray95")) +
    geom_vline(xintercept = mean(d$x, nna.rm = TRUE), color = "red") +
    geom_vline(xintercept = median(d$x, na.rm = TRUE), color = "blue")
  # Add annotation for NA's
  if(nas > 0){
    density <- density + ggtitle(title, subtitle = paste(nas, "Null Observations")) 
  }

  # Create a scatter plot
  scatter <- ggplot(d, aes(x, TARGET_WINS)) +
    geom_point() + 
    labs(x = xlab,
         y = ylab) +
    expand_limits(y=0) +
    theme(panel.background = element_blank(),
          panel.grid.major = element_line(color = "gray95"))
  # Put them side by side
  grid.arrange(density, scatter, ncol=2)
}
```

>>>>

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

@@

```{r}
plot_me <- function(d, title, xlab, ylab){
  nas <- d %>% filter(is.na(x)) %>% nrow()
  density <- d %>%
    filter(!is.na(x)) %>%
    ggplot(., aes(x, stat(count))) +
    geom_density() +
    labs(title = title, 
       x = xlab,
       y = ylab) +
    theme(panel.background = element_blank(),
        panel.grid.major = element_line(color = "gray95")) +
    geom_vline(xintercept = mean(d$x, na.rm = TRUE), color = "red") +
    geom_vline(xintercept = median(d$x, na.rm = TRUE), color = "blue")
  # Add annotation for NA's
  if(nas > 0){
    density <- density + ggtitle(title, subtitle = paste(nas, "Null Observations")) 
  }

  # Create a scatter plot
  scatter <- ggplot(d, aes(x, TARGET_WINS)) +
    geom_point() + 
    geom_smooth(method = lm) + 
    labs(x = xlab,
         y = ylab) +
    expand_limits(y=0) +
    theme(panel.background = element_blank(),
          panel.grid.major = element_line(color = "gray95"))
  # Put them side by side
  grid.arrange(density, scatter, ncol=2)
}
```
